### 2014-06-06 method.tex
Corrected caption and multi-label training

@@

For the quick-to-compute feature, we consider statistics about ROI location and overlap with other regions, as described in \autoref{sec:region}; whole-image CNN pixel gradient in \autoref{sec:gradient}, and an amortized R-CNN variant that operates on a feature pyramid in \autoref{sec:dense}.
The Cascaded CNN is described in \autoref{sec:ccnn}.
The region selection is explained in \autoref{sec:dynamic}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Region statistics}\label{sec:region}

We compute a very simple feature for each ROI: its normalized location,
its scale($\sqrt{\text{width} \times \text{height}}$),
aspect ratio ($\log \sqrt{\text{width} / \text{height}}$),
and normalized counts of overlapping regions, at different PASCAL overlap \todo{definition} thresholds (0, 0.2, 0.6).

@@

We have fine-tuned an ``AlexNet'' \cite{Krizhevsky-NIPS-2012} CNN using the PASCAL VOC 2007 classification challenge.
Unlike the ILSVRC, the PASCAL VOC is a multi-label prediction task, with at times multiple correct labels for an image.
Accordingly, we implement a simple multi-label loss layer for this fine-tuning.
\todo{@sergio: details needed?}

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.98\columnwidth]{figures/ccnn.pdf}
\caption{
The Cascaded CNN has a reject option after pool1, pool2, conv3 and conv4 layers.
\todo{Redo figure to introduce the Reject layers and color their arrows red to make it clear that a choice is being made.}
}\label{fig:ccnn}
\end{center}
\end{figure}

>>>>

We consider first approaches which can effectively reorder the sequence of regions to maximize the chance that correct detections will be found, based on inference from relatively lightweight features.  We show that basic strategies, such as simply randomly reordering the boxes such that they do not have a degenerate spatial layout, provides a surprising boost, and that very simple features such as region and gradient statistics can provide some signal that is useful to prioritize regions, but that those are relatively weak.  Features based on convolutional mid-level primitives are more powerful, as they are directly related to our final detector.  We consider approximate measures computed from a grid of mid-level features; this proves to be a powerful signal, and provides a clear boost when the time required to compute that feature is not considered.    But even with a fast image pyramid to compute them globally for all regions, the time required is unfortunately large enough to significantly dilute their impact.

What is thus desired is a method which can compute an early feature which indicates the region priority, and then can use that same feature in the subsequent classification, with minimal computation that cannot be so amortized.  We formulate a cascade version of the RCNN architecture which has these desirable properties, and show that either alone or in concert with other of the methods described above, it can effectively learn a "Timely" approach to the detection computation.

}; whole-image CNN pixel gradient in \autoref{sec:gradient}, and an amortized R-CNN variant that operates on a feature pyramid in \autoref{sec:dense}.
The Cascaded CNN is described in \autoref{sec:ccnn}.
The region selection is explained in \autoref{sec:dynamic}.

We first review the base model that our work is derived from, the R-CNN method in the following subsection.  We then present our approach to region prioritization using simple features based on basic region and gradient properties in \autoref{sec:region} and \autoref{sec:gradient}.  We then consider mid-level features in \autoref{sec:dense}, based on a Pyramid scheme which amortizes the computation across overlapping regions, but does not use them for the subsequent computation.  Finally, we present our final model, the Cascade-CNN, in \autoref{sec:ccnn} which combines elements of all of these approaches into a unified scheme: it can prioritize based on low-level features early in the CNN, or mid-level features, and when it has decided to carry the computation to the final detection it does so effectively re-using the computation from the earlier tests, and therefore does not waste additional time. Our region selection method is explained in \autoref{sec:dynamic}.

\subsection{Base model}

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Region statistics}\label{sec:region}
For the quick-to-compute feature, we consider statistics about ROI location and overlap with other regions.
We compute a very simple feature for each ROI: its normalized location,
its scale($\sqrt{\text{width} \times \text{height}}$),
aspect ratio ($\log \sqrt{\text{width} / \text{height}}$),
and normalized counts of overlapping regions, at different PASCAL overlap \todo{definition} thresholds (0, 0.2, 0.6).

@@

We have fine-tuned an ``AlexNet'' \cite{Krizhevsky-NIPS-2012} CNN using the PASCAL VOC 2007 classification challenge.
Unlike the ILSVRC, the PASCAL VOC is a multi-label prediction task, with at times multiple correct labels for an image.
Accordingly, we implement cross-entropy loss layer to train a simple multi-label classifier with binary vector.

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.98\columnwidth]{figures/ccnn.pdf}
\caption{
The Cascaded CNN has a reject option after pool1, pool2 and conv3 layers.
\todo{Redo figure to introduce the Reject layers and color their arrows red to make it clear that a choice is being made.}
}\label{fig:ccnn}
\end{center}
\end{figure}
